%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt,a4paper,]{awesome-cv}

% Configure page margins with geometry
\usepackage{geometry}
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}


% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Sophie Breitbart}{}

\position{Data Scientist}
\address{Toronto, Canada}

\email{\href{mailto:sophie.breitbart@gmail.com}{\nolinkurl{sophie.breitbart@gmail.com}}}
\github{sbreitbart}
\linkedin{sophiebreitbart}
\twitter{SophieBreitbart}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------



% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{2em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\honortitlestyle{#1}}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\honordatestyle{#1}}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {June, 2023}
    {Sophie Breitbart~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{current-employment}{%
\section{Current employment}\label{current-employment}}

\begin{cventries}
    \cventry{Data scientist}{Nectric}{Melbourne, Australia}{Jan. 2019 - Present}{\begin{cvitems}
\item Data science consulting projects including spatio-temporal modelling, and large scale forecasting.
\item Hosting workshops improving data literacy, development, analysis and modelling capabilities.
\end{cvitems}}
    \cventry{Research assistant}{Monash University}{Clayton, Australia}{Oct. 2015 - Present}{\begin{cvitems}
\item Involved in many internal and external data projects of varying size and complexity.
\item Projects typically feature large scale time series modelling or analysis, cross-sectional modelling and creating tools for improving workflows.
\item Consulting project clients include: COVID-19 Doherty Institute, Huawei, Monash University, R Consortium, and the NSW Chief Scientist office.
\item Developer for The R Journal, producing software for managing submitted articles and publishing them in both interactive HTML and static PDF.
\end{cvitems}}
    \cventry{Teaching Associate}{Monash University}{Clayton, Australia}{Mar. 2016 - Present}{\begin{cvitems}
\item Sessional teaching of university students undertaking Bachelor's and Master's degrees. Specific classes are listed in 'Teaching experience'.
\end{cvitems}}
\end{cventries}

\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{BCom (Hons) in Econometrics}{Monash University}{Clayton, Australia}{Mar. 2017 - Nov. 2017}{\begin{cvitems}
\item Recipient of the Econometrics Honours Memorial Scholarship, Dean's Honour, Dean's Commendation, and best in class for 5 units.
\item Honours research project was to develop a state space model for quickly forecasting time series with multiple seasonalities.
\item Studied units include Bayesian and frequentist econometrics, advanced statistical modelling and computational science.
\end{cvitems}}
    \cventry{BCom in Econometrics, BSc in Mathematical statistics and Computational Science}{Monash University}{Clayton, Australia}{Mar. 2013 - Nov. 2016}{\begin{cvitems}
\item Recipient of the Monash Community Leaders Scholarship, International Institute of Forecasters Award, and best in class for 4 units.
\item Mentor for the Access Monash Ambassador Program (2015 and 2016)
\item Participant of the Vice-Chancellor's Ancora Imparo Student Leadership Program (2014)
\item Studied a broad range of units covering many aspects of data science. The three disciplines I majored in explored different perspectives for working with data.
\end{cvitems}}
\end{cventries}

\hypertarget{teaching-experience}{%
\section{Teaching experience}\label{teaching-experience}}

\hypertarget{university-tutoring}{%
\subsection{University Tutoring}\label{university-tutoring}}

\begin{cvhonors}
    \cvhonor{}{\textbf{ETC3550/ETC5550}: Applied forecasting (Monash Clayton)}{}{2022 S1}
    \cvhonor{}{\textbf{ETC5523}: Communicating with Data (Monash Clayton)}{}{2021 S2}
    \cvhonor{}{\textbf{ETC3550/ETC5550}: Applied forecasting (Monash Clayton)}{}{2021 S1}
    \cvhonor{}{\textbf{ETC5523}: Communicating with Data (Monash Clayton)}{}{2020 S2}
    \cvhonor{}{\textbf{ETC3550/ETC5550}: Applied forecasting (Monash Clayton)}{}{2020 S1}
    \cvhonor{}{\textbf{ETC3580}: Advanced statistical modelling (Monash Clayton)}{}{2019 S2}
    \cvhonor{}{\textbf{ETC1010}: Data modelling and computing (Monash Clayton)}{}{2019 S2}
    \cvhonor{}{\textbf{ETC1010}: Data modelling and computing (Monash Clayton)}{}{2019 S1}
    \cvhonor{}{\textbf{ETC3550/ETC5550}: Applied forecasting for business and economics (Monash Clayton)}{}{2019 S1}
    \cvhonor{}{\textbf{ETC1010}: Data modelling and computing (Monash Clayton)}{}{2018 S2}
    \cvhonor{}{\textbf{ETC3580}: Advanced statistical modelling (Monash Clayton)}{}{2018 S2}
    \cvhonor{}{\textbf{ETF3231/ETF5231}: Business forecasting (Monash Caulfield)}{}{2018 S1}
    \cvhonor{}{\textbf{ETC1010}: Data modelling and computing (Monash Clayton)}{}{2017 S2}
    \cvhonor{}{\textbf{ETF3231/ETF5231}: Business forecasting (Monash Caulfield)}{}{2017 S1}
    \cvhonor{}{\textbf{ETF2700}: Mathematics for business (Monash Caulfield)}{}{2016 S2}
    \cvhonor{}{\textbf{ETF3231/ETF5231}: Business forecasting (Monash Caulfield)}{}{2016 S1}
\end{cvhonors}

\newpage

\hypertarget{industry-workshops}{%
\subsection{Industry Workshops}\label{industry-workshops}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Tidy Time Series and Forecasting in R}: Teaching assistant (rstudio::conf, USA) \newline Two day workshop with Rob Hyndman on forecasting using tidyverse workflows.}{}{Jan. 2020\newline}
    \cvhonor{}{\textbf{Interactive documents with Shiny}: Instructor (CSIRO, Australia) \newline Two day intermediate workshop on developing of shiny applications.}{}{Nov. 2019\newline}
    \cvhonor{}{\textbf{Data Wrangling}: Instructor (Monash University, Australia) \newline A short workshop in the 'R Workshops for Beginners' series on using tidyr and dplyr to wrangle data.}{}{Sep. 2019\newline}
    \cvhonor{}{\textbf{Tidyverse developer day}: Helper (RStudio, France) \newline A one day developer day where I helped R users resolve issues on tidyverse packages.}{}{Jul. 2019\newline}
    \cvhonor{}{\textbf{High-dimensional time series analysis}: Teaching assistant (ISI WSC, Malaysia) \newline One day short course with Rob Hyndman for analysing and forecasting large collections of time series.}{}{Aug. 2019\newline}
    \cvhonor{}{\textbf{The grammar of animation}: Instructor (Monash University, Australia) \newline A short workshop for NUMBAT group on creating animated graphics in R with the gganimate package.}{}{Mar. 2019\newline}
    \cvhonor{}{\textbf{Master R Developer Workshop}: Teaching assistant (RStudio, Australia) \newline A two day workshop with Hadley Wicham on programming with R and developing R packages.}{}{Dec. 2016\newline}
\end{cvhonors}

\hypertarget{research-output}{%
\section{Research output}\label{research-output}}

\hypertarget{software}{%
\subsection{Software}\label{software}}

My primary research output is the translation of academic research into
open source software packages.

\begin{cvhonors}
    \cvhonor{}{\textbf{gghdr}: Author \newline Extends ggplot2 with plot types for visualising highest density regions.}{}{2022\newline}
    \cvhonor{}{\textbf{distributional}: Lead developer \newline Vectorised distribution objects with methods for manipulating and computing on probability distributions.}{}{2020\newline}
    \cvhonor{}{\textbf{fable}: Lead developer \newline A collection of time series models for use in a tidyverse workflow.}{}{2019\newline}
    \cvhonor{}{\textbf{fable.prophet}: Lead developer \newline Extension package implementing the prophet forecasting procedure for fable.}{}{2019\newline}
    \cvhonor{}{\textbf{feasts}: Lead developer \newline A collection of features, decompositions, statistics and graphics tools for the analysing tidy time series data.}{}{2019\newline}
    \cvhonor{}{\textbf{fabletools}: Lead developer \newline Provides common utilities for the fable forecasting framework, allows users to extend fable with new models.}{}{2019\newline}
    \cvhonor{}{\textbf{tsibbledata}: Lead developer \newline Diverse datasets in a tidy time series data structure (tsibble). Useful in examples of tidy time series analysis.}{}{2019\newline}
    \cvhonor{}{\textbf{tsfeatures}: Author \newline Various methods for extracting features from time series data.}{}{2019\newline}
    \cvhonor{}{\textbf{tsibble}: Contributor \newline Tidy temporal data structures and tools. The data for the tidy time series collection of packages.}{}{2018\newline}
    \cvhonor{}{\textbf{vitae}: Lead developer \newline Dynamically generate a Résumé or CV using R Markdown. This CV is created using code with that package!}{}{2018\newline}
    \cvhonor{}{\textbf{cransays}: Author \newline Provides a dashboard and historical data for R packages being reviewed by CRAN.}{}{2018\newline}
    \cvhonor{}{\textbf{fasster}: Lead developer \newline Implementation of the FASSTER model for forecasting complex multiple seasonal patterns.}{}{2017\newline}
    \cvhonor{}{\textbf{icons}: Lead developer \newline Embed SVG icons in R documents such as slides, reports and apps.}{}{2017\newline}
    \cvhonor{}{\textbf{taipan}: Lead developer \newline Generates shiny apps for annotating image data, which is useful for training machine learning models.}{}{2018\newline}
    \cvhonor{}{\textbf{ggquiver}: Lead developer \newline Extends ggplot2 for displaying vector fields on plots.}{}{2017\newline}
    \cvhonor{}{\textbf{forecast}: Author \newline Methods and tools analysing univariate time series data and producing model-based forecasts.}{}{2015\newline}
\end{cvhonors}

\newpage

\hypertarget{presentations}{%
\subsection{Presentations}\label{presentations}}

\begin{cvhonors}
    \cvhonor{}{\textbf{Forecasting with multiple seasonality}: Methods and techniques to multiple seasonal forecasting in R \newline \url{https://slides.mitchelloharawild.com/nhs2020/}}{}{2020}
    \cvhonor{}{\textbf{Probabilistic cross-temporal hierarchies}: Recent developments of temporal reconciliation in fable. \newline \url{https://slides.mitchelloharawild.com/isf2020/}}{}{2020}
    \cvhonor{}{\textbf{Flexible futures for fable functionality}: Gradual introduction to tidy forecasting with fable. Flexibility is demonstrated with combination modelling and package extensibilitiy. \newline \url{https://slides.mitchelloharawild.com/fable-tfeam/}}{}{2019}
    \cvhonor{}{\textbf{Flexible futures for fable functionality}: Reconciled forecasting of many time series with model combinations. \newline \url{https://slides.mitchelloharawild.com/isf2019/}}{}{2019}
    \cvhonor{}{\textbf{Tidy forecasting in R}: Discussion of recent developments to the fable framework. \newline \url{https://slides.mitchelloharawild.com/fable-tfeam/}}{}{2018}
    \cvhonor{}{\textbf{Forecasting multiple seasonality with state switching}: The FASSTER model with the fable framework. \newline \url{https://slides.mitchelloharawild.com/user2018}}{}{2018}
    \cvhonor{}{\textbf{Models for forecasting multiple seasonality}: An introduction to the FASSTER model. \newline \url{https://slides.mitchelloharawild.com/melburn17/}}{}{2017}
\end{cvhonors}

\hypertarget{publications}{%
\subsection{Publications}\label{publications}}

\hypertarget{awards-achievements}{%
\section{Awards \& Achievements}\label{awards-achievements}}

\hypertarget{awards}{%
\subsection{Awards}\label{awards}}

\begin{cvhonors}
    \cvhonor{}{Dean’s Citation for Outstanding Contribution to Student Learning as a Teaching Associate}{Monash}{2021}
    \cvhonor{}{Commerce Dean's Honour}{Monash}{2017}
    \cvhonor{}{Commerce Dean's Commendation}{Monash}{2016}
    \cvhonor{}{Science Dean’s List}{Monash}{2014-2016}
    \cvhonor{}{International Institute of Forecasters Award}{IIF}{2014}
    \cvhonor{}{Rotary Youth Leadership Award}{Rotary}{2013}
\end{cvhonors}

\hypertarget{scholarships}{%
\subsection{Scholarships}\label{scholarships}}

\begin{cvhonors}
    \cvhonor{}{Econometrics Honours Memorial Scholarship}{Monash}{2017}
    \cvhonor{}{Monash Community Leaders Scholarship}{Monash}{2015 \& 2016}
    \cvhonor{}{Mitcham Rotary Scholarship}{Rotary}{2011 \& 2012}
\end{cvhonors}

\hypertarget{competitions}{%
\subsection{Competitions}\label{competitions}}

\begin{cvhonors}
    \cvhonor{}{UseR! 2018 Datathon Champion}{UseR!}{2018}
    \cvhonor{}{RMIT SBITL Analytics Competition Champion}{RMIT}{2017}
    \cvhonor{}{RMIT SBITL Analytics Competition Champion}{RMIT}{2016}
\end{cvhonors}



\end{document}
